---
title: "report_title"
author: "Lee Kennedy"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Objective

## Background

## Scope

## Experimental Design

## Linearity

```{r linearity, fig.width=7, fig.height=4, echo = FALSE}

col1 <- colnames(linearity[1])
col2 <- colnames(linearity[2])
colnames(linearity)[1] <- "A"
colnames(linearity)[2] <- "B"

if(is.na(linearity[1,2]) == TRUE) {
        linearity_comment <- "Linearity was not examined."
        
} else {

lin <- lm(linearity$B~linearity$A)
lin1 <- summary(lin)
lin2 <- tidy(lin)
R2 <- lin1$r.squared

options(scipen = 5)

linplot = ggplot(linearity, aes(x = A, y = B)) + 
        geom_point(size=5, shape = 21, colour = "darkgreen") + 
        geom_abline(intercept=coef(lin)[1], slope=coef(lin)[2]) + 
        stat_smooth(method = "lm", fullrange = TRUE) +
        labs(x=col1, y=col2) +
        theme_bw() +
        theme(panel.grid.major = element_line(size = 0.5, color = "grey"), 
              axis.line = element_line(size = 0.7, color = "black"), 
              legend.position = c(2.3,8), 
              text = element_text(size = 14))

plot(linplot)


linearity_comment <- paste("The coefficient of determination was ", round(R2,3),".", sep="")

}

```
**Discussion:**

`r linearity_comment`



## LOD & LOR

The LOD and LOR are estimated from three and ten times the standard deviation of results near the LOR, respectively.

```{r, fig.width=7, fig.height=4, echo=FALSE}

colnames(LOR)[1] <- "Test"
colnames(LOR)[2] <- "Result"

LOR <- na.omit(LOR)

if(is.na(LOR[1,2]) == TRUE) {
        limit_d <- "The LOD was not examined."
        limit_r <- "The LOR was not examined."
} else {
limit_d <- paste("The LOD was calculated to be ", round(3*sd(LOR$Result),0),".", sep = "")
limit_r <- paste("The LOR was calculated to be ", round(10*sd(LOR$Result),0),".", sep = "")
}

```

**Discussion**

`r limit_d`

`r limit_r`


## Repeatability and Reproducibility

```{r, fig.width=7, fig.height=4, echo = FALSE}

if(is.na(data_anova[1,2]) == FALSE) {

        cols <- as.numeric(ncol(data_anova))
        rows <- as.numeric(nrow(data_anova))

        Input <- data_anova[1:rows, 1:cols]

        for (i in 1:cols) {
        Input[,i] = as.numeric(unlist(Input[,i]))
        }
}
```


```{r, fig.width=7, fig.height=4, echo=FALSE}
if(is.na(data_anova[1,2]) == TRUE) {
        
        sdr <- " not determined."
        sdR <- " not determined."
        
} else {

#convert to a two element stack
xs <- na.omit(stack(Input))

# Run ANOVA
anova1 <- aov(values ~ ind, data = xs)

summary(anova1)

TukeyHSD(anova1)

#Repeatability & Interim Precision
mean.sqr <- summary(anova1)[1][[1]][[3]]
ncount <- as.numeric(length(anova1$effects))/as.numeric(length(anova1$coefficients))
sdr <- round(sqrt(mean.sqr[2]),3)
interim <- sqrt((mean.sqr[1]-mean.sqr[2])/ncount)
sdR <- round(sqrt(sdr^2 + interim^2),3)

}
```
Repeatability standard deviation: `r sdr`

Reproducibility standard deviation: `r sdR`

**Discussion**

```{r, fig.width=7, fig.height=4, echo = FALSE}

if(is.na(data_anova[1,2]) == FALSE) {
        
Mean <- mean(xs$values)
UCL <- Mean + 3*sdR
UWL <- Mean + 2*sdR
LWL <- Mean - 2*sdR
LCL <- Mean - 3*sdR

plot_anova = ggplot(xs, aes(x=ind, y=values)) +
        geom_point(size=5, shape = 21, colour = "black", fill = "cornflowerblue") +
        geom_hline(aes(yintercept=Mean),lty=5, col = "blue") +
        geom_hline(aes(yintercept=UCL),lty=5, col = "red") +
        geom_hline(aes(yintercept=LCL),lty=5, col = "red") +
        geom_hline(aes(yintercept=UWL),lty=5, col = "darkgreen") +
        geom_hline(aes(yintercept=LWL),lty=5, col = "darkgreen") +
        scale_y_continuous(limits = c(0.98*LCL,1.02*UCL)) +
        theme_bw() +
        theme(panel.grid.major = element_line(size = 0.5, color = "grey"), 
              axis.line = element_line(size = 0.7, color = "black"), 
              legend.position = c(2.3,8), 
              text = element_text(size = 14))

plot_anova
}
```

## Bias

```{r, fig.width=7, fig.height=4, echo = FALSE}

if(is.na(bias[1,9]) == TRUE) {
        ave_bias <- "[Not examined]"
        UoB <- "[Not examined]"
        signif <- "[Not examined]"
} else {
        
r_bias = nrow(bias)

bias <- na.omit(bias)


u_ref <- mean(bias$pct_sd)/sqrt(mean(bias$n))
ave_bias <- round(mean(bias$pct_Bias),2)
sd_bias <- sd(bias$pct_Bias)
UoB <- round(sqrt(u_ref^2 + sd_bias^2),2)

if(ave_bias > 2*UoB) {
        signif = "significant"
        }else{
        signif = "insignificant"
}
}
```



```{r, fig.width=7, fig.height=4, echo = FALSE}

if(is.na(bias[1,9]) == FALSE) {
bias$row_n <- as.numeric(rownames(bias))

biasplot <- ggplot(bias, aes(x=row_n, y= bias$pct_Bias)) +
        geom_bar(position = "identity", stat = "identity", fill = "cornflowerblue", colour = "blue") +
        labs(title = "Percent Bias\n", y = "pct_Bias", x = "") +
        theme_bw() +
        theme(panel.grid.major = element_line(size = 0.5, color = "grey"), 
              axis.line = element_line(size = 0.7, color = "black"), 
              legend.position = c(2.3,8), 
              text = element_text(size = 14))
biasplot

}
```


**Discussion**


The average percent bias was found to be `r ave_bias`.  

The uncertainty of the bias was found to be `r UoB`.

The bias was deemed to be `r signif`.

# Comparison to other methods

```{r, fig.width=7, fig.height=4, echo = FALSE}

if(is.na(data3[1,2]) == FALSE) {

fit = lm(New ~ Old, data = data3)

summary(fit)

dataplot <- ggplot(data3, aes(x = Old, y = New)) + 
        geom_point(size=5, shape = 21, colour = "grey20", aes(fill = factor(Product))) + 
        scale_fill_discrete(guide = guide_legend(title = "Product")) +
        geom_abline(intercept=coef(fit)[1], slope=coef(fit)[2]) + 
        annotate("text", label = paste("R2 = ",round(summary(fit)$r.squared,digits=4)), x = 7.5, y = 6) +
        geom_smooth(method = "lm") +
        geom_abline(slope=1, intercept = 0, colour = "red", lty = 2) +
        xlab("Old method") +
        ylab("New method") +
        ggtitle("Comparison: Old vs New\n") +
        geom_hline(yintercept = 0) +
        geom_vline(xintercept = 0) +
        theme_bw(base_size = 12, base_family = "Arial") +
        theme(panel.grid.major = element_line(size = 0.5, color = "grey"), 
              axis.line = element_line(size = 0.7, color = "black"), 
              text = element_text(size = 14)) 
print(dataplot)

coefficients(fit) # model coefficients
confint(fit, level=0.95) # CIs for model parameters 
}

```

**Discussion**

## Measurement Uncertainty

## Discussion

## Conclusion

## References